Making Sequential Programs Deterministic

### 2019-03-31 experiments.tex
more passing benchmarks

\begin{table}[]
    \begin{tabular}{|p{1.5cm}|p{1cm}|p{4cm}|p{5cm}|}
        \hline
        Benchmark & Recall? & Error message source & Error msg  \\ \hline
        P1 & Yes & FieldAccess.java: [102,87] & assignment type incompatible \\
        P2 & Yes & YamlWriter.java: [224,28] & cast unsafe  \\
        P3 & Yes & DateTimeZone.java: [731,27] &  return type incompatible \\ 
        P4 & * & Det checker not found  &   \\ 
        P5 & ** & Class.getDeclaredMethods not found &    \\ 
        P6 & Yes & OptionGroup.java: [55,40]  & argument type incompatible \\ 
        P6 & Yes & Option.java: [157,28]  &  assignment type incompatible\\
        P7(test error) & Yes* & checker/ tests/ determinism/P71.java: 5 & return type incompatible \\ 
        P7(2) & Yes & FieldUtils.java: [219,84] & assignment type incompatible \\
        P7(2) & Yes & Reflection ToStringBuilder.java: [543,65]  & assignment type incompatible  \\
        P7(2) & Yes & HashCodeBuilder.java: [193,69]  & assignment type incompatible   \\
        P7(2) & Yes & CompareToBuilder.java: [322,65] & assignment type incompatible   \\
        P7(2) & Yes & EqualsBuilder.java: [419,69]  & assignment type incompatible  \\
        P7 & Yes & FieldUtils.java: [200,69] & assignment type incompatible \\
        P7 & Yes & FieldUtils.java: [219,84] & assignment type incompatible  \\
        P7 & Yes & FieldUtils.java: [240,86] & assignment type incompatible  \\
        P8 & ** & getDeclaredFields not found &   \\
        P9 & Yes & Printers.java: [269,97]  &  enhancedfor type incompatible \\
        P10 & ** & getDeclaredFields not found  &  \\
        P11 & Yes & MapUtils.java: [20,50]   & enhancedfor type incompatible  \\
        P12 & *  & 0 errors &  \\
        P13 & ** & unbuildable handlebars &  \\
        P14 & Yes  & Maps.java: [91,69] & invalid element type   \\
        P15 & Yes & PkiMessageDecoder.java: [144,29]  &  enhancedfor type incompatible  \\
        P16 & Yes & MethodSorter.java: [56,61]  & assignment type incompatible  \\
        P17 & Yes & JSONObject.java: [674,51]  & assignment type incompatible  \\
        P18 & Yes & SubstitutableLoggerTest.java: [67,61]   & enhancedfor type incompatible  \\
        P19 & Yes & DataDictionaryEventSource.java: [73,78]  &  enhancedfor type incompatible  \\
        P20 & Yes & SaverImpl.java: [43,69]  &  return type incompatible  \\
        P21 & * & 0 errors &   \\ \hline
    \end{tabular}
\end{table}

\todo{If there is time, we could do a second case study, on a program that
  NonDex did not find nondeterminism in.  Our hope would be to find
  nondeterminism that NonDex did not.  Choose a small project that is
  maintained (it has recent commits), so we can communicate with the authors.

>>>>

\begin{table}[]
    \begin{tabular}{|p{1.5cm}|p{1cm}|p{4cm}|p{5cm}|}
        \hline
        Benchmark & Recall? & Error message source & Error msg  \\ \hline
        P1 & Yes & FieldAccess.java: [102,87] & assignment type incompatible \\
        P2 & Yes & YamlWriter.java: [224,28] & cast unsafe  \\
        P3 & Yes & DateTimeZone.java: [731,27] &  return type incompatible \\ 
        P4 & * & Det checker not found  &   \\ 
        P5 & ** & Class.getDeclaredMethods not found &    \\ 
        P6 & Yes & OptionGroup.java: [55,40]  & argument type incompatible \\ 
        P6 & Yes & Option.java: [157,28]  &  assignment type incompatible\\
        P7(test error) & Yes* & checker/ tests/ determinism/P71.java: 5 & return type incompatible \\ 
        P7(2) & Yes & FieldUtils.java: [219,84] & assignment type incompatible \\
        P7(2) & Yes & Reflection ToStringBuilder.java: [543,65]  & assignment type incompatible  \\
        P7(2) & Yes & HashCodeBuilder.java: [193,69]  & assignment type incompatible   \\
        P7(2) & Yes & CompareToBuilder.java: [322,65] & assignment type incompatible   \\
        P7(2) & Yes & EqualsBuilder.java: [419,69]  & assignment type incompatible  \\
        P7 & Yes & FieldUtils.java: [200,69] & assignment type incompatible \\
        P7 & Yes & FieldUtils.java: [219,84] & assignment type incompatible  \\
        P7 & Yes & FieldUtils.java: [240,86] & assignment type incompatible  \\
        P8 & ** & getDeclaredFields not found &   \\
        P9 & Yes & Printers.java: [269,97]  &  enhancedfor type incompatible \\
        P10 & ** & getDeclaredFields not found  &  \\
        P11 & Yes & MapUtils.java: [20,50]   & enhancedfor type incompatible  \\
        P12 & Yes  & GSLayerEncoder21.java: [113,91]  & enhancedfor type incompatible \\
        P13 & ** & unbuildable handlebars &  \\
        P14 & Yes  & Maps.java: [91,69] & invalid element type   \\
        P15 & Yes & PkiMessageDecoder.java: [144,29]  &  enhancedfor type incompatible  \\
        P16 & Yes & MethodSorter.java: [56,61]  & assignment type incompatible  \\
        P17 & Yes & JSONObject.java: [674,51]  & assignment type incompatible  \\
        P18 & Yes & SubstitutableLoggerTest.java: [67,61]   & enhancedfor type incompatible  \\
        P19 & Yes & DataDictionaryEventSource.java: [73,78]  &  enhancedfor type incompatible  \\
        P20 & Yes & SaverImpl.java: [43,69]  &  return type incompatible  \\
        P21 & Yes & RestDocumentation.java: [419,50] &  argument type incompatible   \\ \hline
    \end{tabular}
\end{table}

\todo{If there is time, we could do a second case study, on a program that
  NonDex did not find nondeterminism in.  Our hope would be to find
  nondeterminism that NonDex did not.  Choose a small project that is
  maintained (it has recent commits), so we can communicate with the authors.}

\section{deflaker case study}
\begin{table}[]
    \begin{tabular}{|l|l|}
        \hline
        Benchmark, issue & found by det checker? \\ \hline
        achilles, [2] issue \#309 &  Race condition\\ \hline
        achilles, [3] issue \#310 & Same fix for \#309 and \#310 \\ \hline
        checkstyle [4] issue \#4664& det checker not found \\ \hline
        jackrabbit-oak [6] \#6512&  Unresolved on issue tracker \\ \hline
        jackrabbit-oak [7] issue \#6524&  Dead link, didn't find 6524 in issue tracker \\ \hline
        nutz [10] issue \#1283 &  Removed tests (Printing (HTTP's) Response.getstatus())\\ \hline
        togglz [19] issue \#223 & (use NONDEX for debugging) \\ \hline
        togglz [20] issue \#240 &  \\ \hline
    \end{tabular}
\end{table}
